CAT-DWAM, A Question Answering System

### 2011-05-07 paper/paper.tex
experiment design

\section{Results}
\begin{table}
\begin{tabular}{lcc}
%\toprule
\cmidrule{2-3}
                     & Number correct & Mean recipricol rank\\
\cmidrule{2-3}
Punctuation location &                &                     \\
Novelty factor       &                &                     \\
Both                 &                &                     \\
\cmidrule{2-3}
%\bottomrule
\end{tabular}
%\caption{\label{tab:results}Results of our system on ``Where''-type questions. 
\end{table}
% we need:
% the output file of answers produced by our system for the questions
% from the development corpus
% an evaluation using the Mean Reciprocal Rank Evaulation Measure)
% an analysis of the system's performance on questions of the
% development corpus
   % what worked?
   % what didn't work?
   % which component was strongest/weakest?
   % how does our system compare to the baseline?
% responses from our system for test set released on Wednesday
   % we also need to submit this file

>>>>

\section{Experiment design}
For our experiment, we tried a few runs of the system. We ran the system with
punctuation location on, novelty factor on and both on.
%We repeated each of these for two training corpus sizes: 9 questions and 24 questions.
We tested our models on two test questions and measured the number correct and
mean recipricol rank for the test questions. Both of these measures were zero
for all system variates (table \ref{tab:results}).

\section{Results}
\begin{table}
\begin{tabular}{llcc}
%\toprule
\cmidrule{2-4}
               &       & Number correct & Mean recipricol rank\\
\cmidrule{2-4}
9 Training&Punctuation location &   0            &      0              \\
questions&Novelty factor       &    0           &       0             \\
&Both                 &             0  &                0    \\
\cmidrule{2-4}
24 Training&Punctuation location &                &                     \\
questions&Novelty factor       &                &                     \\
&Both                 &                &                     \\
\cmidrule{2-4}
%\bottomrule
\end{tabular}
\caption{\label{tab:results}Results of our system on ``Where''-type questions. }
\end{table}
% we need:
% the output file of answers produced by our system for the questions
% from the development corpus
% an evaluation using the Mean Reciprocal Rank Evaulation Measure)
% an analysis of the system's performance on questions of the
% development corpus
   % what worked?
   % what didn't work?
   % which component was strongest/weakest?
   % how does our system compare to the baseline?
% responses from our system for test set released on Wednesday
   % we also need to submit this file
